% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=0mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[matt-campbell]{Matt Campbell}

\thinrule

\startblockquote
\startblockquote
\startblockquote
I am a highly dedicated software developer with 5 years commercial
development experience working with PHP (Laravel) and in more recent
years with tools like Ansible, Docker and Terraform. I graduated with a
2:1 in BSc (Hons) Computing at Plymouth University in September 2013 and
started my professional career in 2014.
\stopblockquote
\stopblockquote
\stopblockquote

\thinrule

\subsection[profile]{Profile}

\startitemize[packed]
\item
  Strong communication skills, both written and verbally.
\item
  Good people skills and can develop great working relationships.
\item
  A real believer of \quotation{do something manually twice, automate
  via scripting, if you can}.
\item
  I believe I possess a positive attitude and have a passion for
  expanding my knowledge.
\item
  Experience working in an Agile team environment, with daily standups,
  sprint planning/refinement and retrospective meetings.
\stopitemize

\subsection[education]{Education}

\startdescription{2011-2013}
  {\bf BSc, Computing}; University of Plymouth (2:1)
\stopdescription

\startitemize[packed]
\item
  {\em Final year project {\bf (First Class Grade)}: PHP based web
  application -- tool for communication between project group peers}
\item
  {\em Group project {\bf (First Class Grade)} -- As a group we
  developed a multi-platform photo sharing system.}
\stopitemize

\startdescription{2009-2011}
  {\bf HND, Computing (Level 5)}; Uxbridge College

  {\bf GCSE English (B)}; Uxbridge College

  {\bf CCNA Networking Academy - Semesters 1 & 2 (Pass)}; Uxbridge
  College
\stopdescription

GCSE Maths A.

Received Higher Education award - presented at the
\useURL[url1][http://www.uxbridge.ac.uk/college-news-a-events/414-september-2011/3396-annual-awards-winners-honoured-by-the-apprentices-melody-hossaini.html][][Uxbridge
College awards ceremony 2011]\from[url1].

\subsection[experience]{Experience}

\startdescription{2015-present}
  {\bf Shopworks} - Developer
\stopdescription

Throughout my time at Shopworks I have helped on-board several new
developers into the team.

\startitemize[packed]
\item
  Involved with undertaking code review for other team members.
\item
  Vast experience with combining legacy code written in CodeIgniter with
  a more OOP style in Laravel.
\item
  Comfortable with a TDD approach to solving problems.
\item
  Developed skills with automated deployments and DevOps with tools like
  Ansible, Terraform and Docker.
\item
  Comfortable with new site setup and server administration, from server
  setup using Ansible, or things like SSL renewal.
\item
  Very comfortable with Git and advanced features like pull request
  workflows, rebasing and following recommended
  \useURL[url2][https://chris.beams.io/posts/git-commit/][][commit
  message guidelines]\from[url2].
\item
  Experience and passion for improving internal wiki documentation,
  which you can read about
  \useURL[url3][https://mcampbell508.github.io/2017/12/17/recommended-documentation-for-a-web-team/][][here]\from[url3].
\stopitemize

\startdescription{2014-2015}
  {\bf YourParkingSpace} - Developer
\stopdescription

Starting as an intern for 3 months in my first development role, I was
offered a permanent role after a very successful internship. Working in
a small team, I established myself as a valued member of a close-knit
team. Working with another co-developer, my duties included making day
to day improvements to the company web application, fixing bugs and
adding new features.

\startitemize[packed]
\item
  Day-to-day bug fixing, and implementing new feature requests.
\item
  Git experience improved, working in a pull request development cycle.
\item
  Always part of technical discussions within the team for on-going
  improvements.
\item
  Involved with migration to SSL site version.
\item
  Implementation of Stripe payments API within an instant payment
  system.
\stopitemize

\subsection[technical-experience]{Technical Experience}

Open Source

\startitemize[packed]
\item
  \useURL[url4][https://github.com/mcampbell508/ansible-phpstorm][][Ansible
  role for installing PhpStorm]\from[url4], which I developed to help
  automate the installation of new versions.
\item
  \useURL[url5][https://github.com/mcampbell508/mcampbell508.github.io][][Personal
  blog and resume]\from[url5] are written in markdown and easily
  converted to multiple formats (HTML, Pdf, Doc)
\stopitemize

\startdescription{Programming Languages / Skills}
  {\bf PHP:} Very confident with this language and the new features
  available in PHP 7.

  {\bf Ansible:} A lot of experience with this tool in terms of
  provisioning and using it for deployments.

  {\bf Docker:} I am aware of the importance of containers, and the role
  this can play with making scalable applications.

  Basic knowledge of {\bf VueJS}, {\bf React JS}
\stopdescription

\startitemize[packed]
\item
  Laravel, CodeIgniter OOP, PHP 7, TDD, MySQL, DNS, Virtual Host,
  Apache, Ansible, Deployer PHP, Markdown, Ubuntu, CentOS, VirtualBox,
  Vagrant, Wikis, Bash, Git, Git Hooks
\stopitemize

\thinrule

\startblockquote
\useURL[url6][mailto:matthewcampbell508@gmail.com][][matthewcampbell508@gmail.com]\from[url6]
Uxbridge, Middlesex\crlf
\useURL[url7][https://mcampbell508.github.io]\from[url7]
\stopblockquote

\stoptext
